analysis-pilot

### 2023-08-19 code/analysis-pilot.Rmd
dimensions of graph

ggplot(timed_speaker, aes(x = trialNum-1, y = totwordCount)) + 
  geom_line(aes(group=game)) +
  geom_smooth() +
  labs(color = "Game ID", x = "\nTrial", y = "Word Count\n") +
  scale_x_continuous(breaks=seq(1,12,1), limits = c(1,12)) +
  theme_classic() +
  theme(aspect.ratio = 9/9,
        axis.title=element_text(size=14,face="bold"),
        axis.text=element_text(size=9, color = "black"),
        legend.title=element_text(size=13,face="bold"),
        legend.text=element_text(size=9),
        legend.position="right")
ggsave("SpeakerWord.png")
```

@@

ggplot(timed_listener, aes(x = trialNum-1, y = totwordCount)) + 
  geom_line(aes(group=game)) +
  geom_smooth() +
  labs(color = "Game ID", x = "\nTrial", y = "Word Count\n") +
  scale_x_continuous(breaks=seq(1,12,1), limits = c(1,12)) +
  theme_classic() +
  theme(aspect.ratio = 9/9,
        axis.title=element_text(size=14,face="bold"),
        axis.text=element_text(size=9, color = "black"),
        legend.title=element_text(size=13,face="bold"),
        legend.text=element_text(size=9),
        legend.position="right")
ggsave("ListenerWord.png")
```

>>>>

ggplot(timed_speaker, aes(x = trialNum-1, y = totwordCount)) + 
  geom_line(aes(group=game)) +
  geom_smooth() +
  labs(color = "Game ID", x = "\nTrial", y = "Word Count\n") +
  scale_x_continuous(breaks=seq(1,12,1), limits = c(1,12)) +
  theme_classic() +
  theme(aspect.ratio = 7/9,
        axis.title=element_text(size=14,face="bold"),
        axis.text=element_text(size=9, color = "black"),
        legend.title=element_text(size=13,face="bold"),
        legend.text=element_text(size=9),
        legend.position="right")
ggsave("SpeakerWord.png")
```

@@

ggplot(timed_listener, aes(x = trialNum-1, y = totwordCount)) + 
  geom_line(aes(group=game)) +
  geom_smooth() +
  labs(color = "Game ID", x = "\nTrial", y = "Word Count\n") +
  scale_x_continuous(breaks=seq(1,12,1), limits = c(1,12)) +
  theme_classic() +
  theme(aspect.ratio = 7/9,
        axis.title=element_text(size=14,face="bold"),
        axis.text=element_text(size=9, color = "black"),
        legend.title=element_text(size=13,face="bold"),
        legend.text=element_text(size=9),
        legend.position="right")
ggsave("ListenerWord.png")
```
